# Data transformation
```{r setup, include=FALSE}
 # keep this chunk in your .Rmd file
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

From the New York State government website, we download the open NY data directly from the electric vehicle charging station map section web link. We then use the downloaded data set directly as a dataframe. 

To clean the data, we will drop irrelevant columns and check for duplicate rows. 

We will change the types to appropriate ones for the primary features we are going to focus on. For example, features such as city, state, EV connector types are in characters and we may need to convert them to factor data to better fit the desired graph; the dates information are also stored in character format, and we will transfer them to date formats.

Also, in the next section, we will work on dealing with the missing values. we will check whether there are certain patterns in the empty columns and rows, and drop those unnecessary entries.


```{r stations, include=FALSE}
library(tidyverse)
library(rvest)
library(robotstxt)
library(pander)
library(readxl)
#paths_allowed("https://data.ny.gov/api/views/7rrd-248n/rows.csv?accessType=DOWNLOAD&sorting=true")
stations <-read.csv("https://data.ny.gov/api/views/7rrd-248n/rows.csv?accessType=DOWNLOAD&sorting=true")
registration_url<-"https://www.nyserda.ny.gov/-/media/Files/Programs/ChargeNY/EV-Registration-Tables.xlsx"
temp <-tempfile(fileext = ".xlsx")
download.file(registration_url, destfile=temp, mode='wb')
registration_utility <- readxl::read_excel(temp, sheet =1)
registration_zipcode <- readxl::read_excel(temp, sheet =2)
registration_model <- readxl::read_excel(temp, sheet =3)
registration_county <- readxl::read_excel(temp, sheet =4)
registration_originaltime <- readxl::read_excel(temp, sheet =5)
registration_originalmake <- readxl::read_excel(temp, sheet =6)
```




<p style="font-size:23px;"> EV Charging Stations Info </p>
```{r}
## drop 3 columns with only NA values, will drop more irrelevant columns. Fuel Type Code has ELEV only. State has NY only. Status Code has E only
stations <- stations %>%
      select(- c("Plus4", "Expected.Date", "EV.Other.Info","Fuel.Type.Code","State","Station.Phone","Status.Code"))
```


Charging Stations Access Days Time
```{r}
stations$hours <- ifelse(grepl("24", stations$Access.Days.Time), "24hr", "other")
pie(table(stations$hours),col=grey.colors(2))
```
     
Charging Stations Owners
```{r}
ownerlist<-data.frame(table(stations$Owner.Type.Code[stations$Owner.Type.Code!=""]))
colnames(ownerlist)<-c("Owner_Type","Freq")
ownerlist$Owner_Type<-recode(ownerlist$Owner_Type,
  "FG" = "Federal government owned",
  "J" = "Jointly owned",
  "LG"="Local government owned",
  "P"="Privately owned",
  "SG"="State government owned",
  "T"="Utility owned"
)
ggplot(ownerlist, aes(x="", y=Freq, fill=Owner_Type)) +
 geom_bar(stat="identity", width=1) +
 coord_polar("y", start=0) +
  theme_void()
```



<p style="font-size:23px;"> EV Registration Info </p>
#Utility, original time and make may not be useful for our project.

Popular model ranking
```{r}
registration_modelname<-unite(registration_model, modelname, Make:Model, sep='-')[rev(order(registration_model$Registrations)),][-1,]
ggplot(registration_modelname, aes(x = reorder(`modelname`,-`Registrations`), y = `Registrations`)) +
  geom_col(position = "dodge")+theme(axis.text.x=element_text(angle=90, hjust=1))+labs(x="Make-Model")
```


County ranking
```{r}
sortedcounty<-registration_county[rev(order(registration_county$`Total EVs`)),][-1,]
ggplot(sortedcounty, aes(x = reorder(`County`,-`Total EVs`), y = `Total EVs`)) +
  geom_col(position = "dodge")+theme(axis.text.x=element_text(angle=90, hjust=1))+labs(x="County")
```

Zipcode heatmap 
```{r}
library(choroplethrZip)
library(mapproj)

zip_group <- stations %>%
  group_by(ZIP)%>%
  summarize(Count=n())

colnames(zip_group) <- c("region", "value")
zip_group['region']=as.character(zip_group$region)

zip_choropleth(zip_group, 
               state_zoom = "new york", 
               title      = "Draw a heatmap by zip",
               legend     = "Population") + coord_map()  

```

```{r}
temp <- registration_originaltime[1:nrow(registration_originaltime)-1,]
temp  <- temp  %>%
  group_by(Year)%>%
  summarize(total_EV=sum(`Total EVs`))
ggplot(temp, aes(x=Year, y=total_EV))+geom_col()+ ggtitle('Number of Total EV by Years') + xlab("Year")+ylab("Number of Total EV")
```







